\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles

### 2023-11-15 Manuscript/escheR_BioAdv_clean.tex
Clean up ref
typo

\newcommand{\rr}[1]{{\color{red} #1}}
\usepackage{setspace}
\doublespacing

@@

\begin{figure*}[!t]
\begin{center}
\includegraphics[width=\textwidth]{Manuscript/figure/insitu.jpg}
\caption{\small \textbf{\texttt{escheR} enables multi-dimensional spatial visualizations following the Gestalt principles of design}. (\textbf{A-B}) The traditional visualization displays the colocalization plot of the expression of two genes \textit{EFNA5} and \textit{EPHA5} (\textbf{A}) and the spatial domains from the dorsolateral prefrontal cortex in postmorteum human brain \citep{huukimyers_2023} (\textbf{B}) side-by-side, creating challenges to cognitively connecting colocalization status to spatial domains. (\textbf{C}) The watercolor effect enables displaying spatial domains by color-coding only outlines of circles. (\textbf{D}) \texttt{escheR} enables the multi-dimensional \textit{in situ} visualization that simultaneously displays the cortex layers and the colocalization status, substantially improving interpretability.}
\label{fig:visual} 
\end{center}
\vspace{-0.3in}
\end{figure*}

>>>>

\usepackage{setspace}
\doublespacing

@@

\begin{figure*}[!t]
\begin{center}
\includegraphics[width=\textwidth]{Manuscript/figure/insitu.jpg}
\caption{\small \textbf{\texttt{escheR} enables multi-dimensional spatial visualizations following the Gestalt principles of design}. (\textbf{A-B}) The traditional visualization displays the colocalization plot of the expression of two genes \textit{EFNA5} and \textit{EPHA5} (\textbf{A}) and the spatial domains from the dorsolateral prefrontal cortex in postmortem human brain \citep{huukimyers_2023} (\textbf{B}) side-by-side, creating challenges to cognitively connecting colocalization status to spatial domains. (\textbf{C}) The watercolor effect enables displaying spatial domains by color-coding only outlines of circles. (\textbf{D}) \texttt{escheR} enables the multi-dimensional \textit{in situ} visualization that simultaneously displays the cortex layers and the colocalization status, substantially improving interpretability.}
\label{fig:visual} 
\end{center}
\vspace{-0.3in}
\end{figure*}
